Tourism Data Analysis

### 2019-08-22 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd

DF_BoxCoxTrans_Tot_h1 %>% 
  mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
  geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
  ylab("Forecasts/Actual") + 
  ggtitle("Forecasts follow from BoxCox Transformation") + 
  theme(legend.position="bottom")

@@

for (j in 1:140) {#C=140

  Train <- AllTS_new[j:(100+j-1), "Total"] %>% as.ts()

  lambda[j] <- BoxCox.lambda(Train)

}
```

>>>>

DF_BoxCoxTrans_Tot_h1 %>% 
  mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
  geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
  ylab("Forecasts/Actual") + 
  ggtitle("Forecasts follow from BoxCox Transformation") + 
  theme(legend.position="bottom", legend.title = element_blank())

@@

# for (j in 1:140) {#C=140
#   
#   Train <- AllTS_new[j:(100+j-1), "Total"] %>% as.ts()
# 
#   lambda[j] <- BoxCox.lambda(Train)
#   
#   
# }

j = 130
Train <- AllTS_new[j:(100+j-1), "Total"] %>% as.ts()

fit <- auto.arima(Train, lambda = "auto")
summary(fit)
```
